A new type of generic, self-evolving and efficient automated deduction algorithm based on category theory

### 2023-05-25 proof/Math-7081/Math-7081 proof/Math-7081.tex
PROOF

%% Copyright 2022 Zijian Wang. All rights reserved.
%% Email: felix_wzj@yahoo.com
%% The newest version can be obtained from GitHub.

\documentclass{aims}

%% \special{dvipdfmx:config z 0} %% speed boost
\usepackage{txfonts, verbatim}
\usepackage{amsmath}	%% math part 1
\usepackage{flexisym, breqn}	%% math part 2
\usepackage{amssymb, graphics, setspace}	%% math part 3
\usepackage{tikz, tikz-cd}	%% for commutative diagrams
\usepackage{flowchart}	%% for flowchart
\usepackage{float, booktabs}	%% for table & alignment
\usepackage{algorithmicx, algorithm, algpseudocode}	%% for pseudo code composition
\usepackage{blindtext}	%% overfull hbox solution
\usepackage{setspace}	%% double spacing
\usepackage{url}	%% for reference 9
\usepackage[pagewise]{lineno}\linenumbers
\usepackage[comma, square, sort, numbers]{natbib}

@@

\renewcommand{\bibnumfmt}[1]{[#1]}

\def\typeofarticle{Research article}
\def\currentvolume{}
\def\currentissue{}
\def\currentyear{}
\def\currentmonth{}
\def\ppages{}
\def\DOI{}
\def\Received{}
\def\Revised{}
\def\Accepted{}
\def\Published{}

@@

%\pdfminorversion=7

%\bibliographystyle{unsrt}

\begin{document}
	\title{A new type of generic, self-evolving and efficient automated deduction algorithm based on category theory}
	\author{%
		Zijian Wang\affil{1}
		Shao Xinhui\affil{2,*}
	}
	\shortauthors{the Authors}
	\address{%
		\addr{\affilnum{1}}{Northeast Yucai School, Zhenxing St. 9-5, Heping District, Shenyang, Liaoning, P.R.China.}
		\addr{\affilnum{2}}{Department of Mathematics, College of Sciences, Northerneastern University, Shenyang, Liaoning, P.R.China. }
		\corraddr{Email: shaoxinhui@mail.neu.edu.cn}
	}

	\begin{abstract}
	In this article a new type of generalized, self-evolving and efficient automated statement proof algorithm based on new data structures, i.e. brackets and map graphs
	and new algorithms is presented. The brackets structure provides an elegant low-knowledge representation of mathematical concepts. The map graphs offer an efficient machine-learning method which let the computer learn knowledge while proving. Additionally, the new finding is totally built on the category theory. Furthermore, a prototype of the program is given and examined for performance.
	\end{abstract}

	\keywords{
		\textbf{automatic prover, theorem prover, algorithm, category theory, automatic deduction, automatic reasoning}
		\newline
		\textbf{Mathematics Subject Classification:} 03B35, 68V15, 18-00, 18-04, 68W99
	}

@@

	\section{Introduction}
	During the long period of development of the research on automated theorem provers, there have already existed a great number of research and implementation on proofs focusing on a specific mathematical subject, such as algebra equations (for example, Wolfram Mathematica{'}s FindEquationProof function \cite{Wolfram2019}) or geometrical theorems (for example, the Geometry Expert or GEX \cite{Gao1998} of Key Laboratory of Mathematics Mechanization, Chinese Academy of Sciences). Some relatively new works in this aspect includes Microsoft{'}s Lean prover \cite{Moura2021} and Z3 \cite{Moura2008} algorithm.

@@

	When we humans think of mathematical problems and perform proofs, we do not follow purely logical ways like complex stuff like Cooper{'}s algorithm. Instead, we just perform tries to seek breakthrough points using his knowledge in a diversified thought. Why cannot programs do things like that? Why can not they perform some sort of knowledge transferring? Carry this question and in experimental and curious attitude, we conducted the research on this topic and have found a utility to do the task: the category theory.

@@

	\textit{ Structure of the paper.}\newline
	The paper mainly consists of seven sections. The Introduction section demonstrates the background of the research and fundamental opinions around it. The Preliminaries section, made up of two subsections, claims to minimized pre-knowledge required to understand the paper and the symbols we select to use. The third section defines a set of mathematical structures that will be used by the algorithm. The forth section explains the detailed workflow procedures of the algorithm. The next section claims the conclusions of the research and the to-do improvements in the future. Then the algorithm is examined using several experiments and benchmarks to test the performance through the corresponding computer program in the thereupon. Finally the Acknowledgments section expresses my gratitude to the help and the References section claims the referential resources used while conducting the project.

@@

	\subsection{Notations and Conventions}

@@

	To avoid misunderstandings, \textbf{the Zermelo-Fraenkel set theory} or ZFC as short is utilized to be the set system, with Grothendieck universe concepts added. \cite{Li2019}

@@

	\subsection{Pre-Knowledge}

@@

	%%\pmb{ Axiom.} The Selection Axiom.
	\begin{axiom}
		The Selection Axiom.

@@

	%%\pmb{ Theorem. }
	\begin{theorem}
		The Zermelo{'}s Well-Ordering Theorem.\cite{Li2019}

@@

	\begin{equation*}
		X_{n+1}=(\left(a X_n+c\right) \bmod M)
	\end{equation*}

@@

	\begin{equation*}
		M=2^{32},a=1103515245, c=12345
	\end{equation*}

@@

	\section{The Computerized Representation of Mathem-atical Structures}

	Before more specific discussion, we select Grothendieck universe \(\mathcal{U}\) \cite{Li2019} to avoid set theory paradoxes. Besides, we define meta category \(\mathcal{C}\) where all discussions take place. There are briefly three kind of objects in \(\mathcal{C}\): symbols, notations and brackets. All symbols in \(\mathcal{C}\) forms sub-category \(\text{Sym}(\mathcal{C})\) called the \textbf{ Symbol Subcategory}. All notations in \(\mathcal{C}\) forms \(\text{Not}(\mathcal{C})\) and all brackets forms \(\text{Bra}(\mathcal{C})\), called the \textbf{ Notation Subcategory} and the \textbf{ Bracket Subcategory}. That is,

	\begin{equation}
		\mathcal{C}=\text{Sym}(\mathcal{C})\cup \text{Not}(\mathcal{C})\cup \text{Bra}(\mathcal{C})
	\end{equation}

@@

	%% \pmb{ Definition.} 
	\begin{definition}
		A \textbf{ bracket} \(\beta\) is defined as a set of ordered pairs in the form of below:

		\begin{equation}
			\beta \text{:=}\left\{(i,x)\left|i\in \text{On}_{\geq 1}\right.,x\in \text{Sym}(\mathcal{C})\cup \text{Not}(\mathcal{C})\cup \text{Bra}(\mathcal{C})\right\}
		\end{equation}

		\(\beta\) is valid if and only if every element of \(\beta\), its left element is unique. We define filtered subsets of \(\beta\). The \textbf{ Symbol Subset} of \(\beta _{\mathcal{S}}\text{:=}\left\{t\in \beta \left|t_{\mathit{r}}\in \text{Sym}(\mathcal{C})\right.\right\}\). Following this way, the \textbf{ Notation Subset} \(\beta _{\mathcal{N}}\) and the \textbf{ Bracket Subset} \(\beta _{\mathcal{B}}\) are defined as well. There are two types of brackets: The first type is called a \textbf{ Symbol Holder} where \(\beta =\{(i,A)\},i\in \mathbb{Z}_{\geq 1},A\in \text{Sym}(\mathcal{C})\). The second type is called a \textbf{ Compositor} where

		\begin{equation}
			\begin{split}
				\beta =\{(j,\mathcal{N})\}\cup \{(i,x)|i\in \text{On}_{\geq 1},\\ x\in \text{Sym}(\mathcal{C})\cup \text{Bra}(\mathcal{C})\},\forall
				t\in \beta ,j\in \text{On}_{[1,t_{\ell }]}\}
			\end{split}
		\end{equation}
	\end{definition}

@@

	%% \pmb{ Definition.} 
	\begin{definition}
		Two bracket \(\alpha\) and \(\beta\), are thought to be \textbf{ isomorphic} (noted as \(\alpha \simeq \beta\)) if they satisfy the following restrictions:

		First, \(|\alpha |=|\beta |\) indicating the two brackets have same cardinal numbers. Second, all right elements sorted in the order defined by the sort of the left pair elements, correspondingly, are either same or symbols with the same type. Otherwise, the two brackets are \textbf{ not isomorphic}, noted as \(\alpha \not{\simeq}\beta\).
	\end{definition}

@@

	%% \pmb{ Definition.} 
	\begin{definition}
		A \textbf{ notation} \(\mathcal{N}\) is defined as an object in \(\text{Not}(\mathcal{C})\) which is a sub-category of \(\mathcal{C}\). The \(\text{Ob}(\text{Not}(\mathcal{C}))\) set can be mapped to \(\text{On}_{\geq 0}\) class, indicating the number of parameters that a notation take. In which,

		\begin{equation}
			\begin{gathered}
				\mathit{p}:\text{Ob}(\text{Not}(\mathcal{C}))\to \text{On}_{\geq 0}\\
				\mathcal{N}\overset{\mathit{p}}{\mapsto}n
			\end{gathered}
		\end{equation}

		In that case if \(n=0\) then we say \(\mathcal{N}\) is a \textbf{ type} and if \(n>0\) then \(\mathcal{N}\) is an \textbf{ operator}. For instance, obviously, \(\mathit{p}(+)=2\) and \(\mathit{p}(\neg )=1\). A notation\(\mathcal{N}\) is called \textbf{ finite} if \(\mathit{p}(\mathcal{N})<\omega\), and otherwise \(\mathcal{N}\) can have infinite number of symbols as parameters, when the notation is called to be \textbf{ infinite}.
	\end{definition}

@@

	%% \pmb{ Definition.}
	\begin{definition}
		A \textbf{ symbol} \(\mathcal{S}\) is defined as an object in \(\text{Sym}(\mathcal{C})\) which is a sub-category of \(\mathcal{C}\). There exists a functor from \(\text{Sym}(\mathcal{C})\) to \(\text{Not}(\mathcal{C})\):

@@

		\noindent where \(\nu (\mathcal{S})\) is the \textbf{ corresponding notation} of \(\mathcal{S}\) and must satisfy \(\forall \mathcal{S}\in \text{Sym}(\mathcal{C}),\mathit{p}(\nu (\mathcal{S}))\) \(= 0\), indicating all corresponding notations are types instead of operators. For convenience and precision, the text that meaning creating a symbol \(\mathcal{S}\) whose corresponding notation is \(\mathcal{N}\)can and should be written in the form below.

		\begin{equation}
			\mathcal{S}\in \text{Ob}(\text{Sym}(\mathcal{C}))\land \mathit{v}(\mathcal{S})==\mathcal{N}
		\end{equation}

@@

		Two brackets are thought to be \textbf{ equal} when the sequences of \(t_{\mathit{r}}\), sorted via the ordering of \(t_{\ell }\) are the same and this relationship constructs a equivalence morphism between the two in the \(\text{Bra}(\mathcal{C})\) category, noted as below:

		\begin{equation}
			\epsilon :\alpha \equiv \beta
		\end{equation}
	\end{definition}

@@

	%% \pmb{ Definition.}
	\begin{definition}
		A notation \(\mathcal{N}\) is called being \textbf{ inherited} from notation \(\mathcal{M}\) (or we say \(\mathcal{N}\) is\textbf{  a kind of} \(\mathcal{M}\)) when there exists such morphism between the two in \(\text{Not}(\mathcal{C})\):

		\begin{equation}
			h\in \text{Mor}(\text{Not}(\mathcal{C})): \mathcal{M}\to \mathcal{N}
		\end{equation}

@@

	\begin{equation*}
		\sum _{n=0}^{\infty } x^n=\frac{1}{1-x}, \text{for} |x|<1
	\end{equation*}

	First, we need to observe what notation is needed by the construction. Apparently, we need to at least define these notations: \(\text{inf}\), \(\text{int}\), \(\text{num}\),\textit{  }\textit{ \(\sum\)}, \(=\), \({}^{\wedge}\), \(/\), \(-\), \(\text{abs}\), \(<\) and \(\text{for}\), where \(\text{abs}\) stands for the absolute value function. However, in this neat example, the concept of function is not needed to be defined. Additionally, as the constructed stuff only needs to demonstrate the equation itself instead of the principles behind the equality, there is no necessity for the definition of notation \(+\). Note that manifestly \(\text{int} \triangleleft | \text{num}\). The table below (\ref{table-1}) demonstrates the number of parameters taken by the notations.

	\begin{table}[h]
		\centering
		\caption{The table for $\mathit{p}(\mathcal{N})$}
		\begin{tabular}{ccccccccccc}
			\toprule
			$\mathcal{N}$ & int & num & inf & $\sum$ & $=$ & $/$ & - & abs & $<$ & for \\
			\midrule
			$\mathit{p}$ & $0$ & $0$ & $0$ & $3$ & $2$ & $2$ & $2$ & $1$ & $2$ & $2$ \\
			\bottomrule
		\end{tabular}
		\label{table-1}
	\end{table}

@@

	\begin{equation*}
		\begin{aligned}
			\pmb{1} &\in& \text{Ob}(\text{Sym}(\mathcal{C}))\land \mathit{v}(\pmb{1})=\text{number}\\
			\pmb{\infty } &\in& \text{Ob}(\text{Sym}(\mathcal{C}))\land \mathit{v}(\pmb{\infty })=\text{infinity}\\
			\pmb{x} &\in& \text{Ob}(\text{Sym}(\mathcal{C}))\land \mathit{v}(\pmb{x})=\text{number}\\
			\pmb{n} &\in& \text{Ob}(\text{Sym}(\mathcal{C}))\land \mathit{v}(\pmb{n})=\text{integer}\triangleleft |\text{number}\\
		\end{aligned}
	\end{equation*}
	\begin{equation*}
		\begin{aligned}
			\alpha &=& \{(0,\text{for}),(1,\beta ),(2,\gamma )\}\\
			\beta &=& \{(0,=),(1,\delta ),(2,\epsilon )\}\\
			\gamma &=& \{(0,<),(1,\zeta ),(2,\pmb{1})\}\\
			\delta &=& \{(0,\sum ),(1,\eta ),(2,\pmb{\infty }), (3,\theta )\}\\
			\epsilon &=& \{(0,/),(1,\pmb{1}),(2,\iota )\}\\
			\zeta &=& \{(0,\text{abs}),(1,\pmb{x})\}\\
			\eta &=& \{(0,=),(1,\pmb{n}),(2,\pmb{1})\}\\
			\theta &=& \{(0,{}^{\wedge}),(1,\pmb{x}),(2,\pmb{n})\}\\
			\iota &=& \{(0,-),(1,\pmb{1}),(2,\pmb{x})\}
		\end{aligned}
	\end{equation*}

@@

	\begin{equation}
		\begin{split}
			\alpha = \{(0,\text{for}),(1,\beta ),(2,\{(0,<),(1,\{(0,\text{abs}),\\(1,\pmb{x})\}),(2,\pmb{1})\})\}\hfill\\
			\beta = \{(0,=),(1,\delta ),(2,\{(0,/),(1,\pmb{1}),(2,\{(0,-),\\(1,\pmb{1}),(2,\pmb{x})\})\})\}\hfill\\
			\delta = \{(0,\sum ),(1,\{(0,=),(1,\pmb{n}),(2,\pmb{1})\}),(2,\pmb{\infty }), (3,\\\{(0,{}^{\wedge}),(1,\pmb{x}),(2,\pmb{n})\})\}\hfill\\
		\end{split}
	\end{equation}

@@

	Another issue is about the recognition between majorly two types of brackets: the type of bracket that purely serves as a brick for constructing mathematical expressions and the type of bracket that forms the thing that former mathematics call them statements (for instance, \(\{(0,=),(1,x),(2,y)\}\) or the expression for the Pythagorean theorem). In this system for representation, the second sort of bracket is called \textbf{ micro-statements}, whose precise definition comes below.

@@

		It is essential to pay attention to that a bracket with 2-parameter notation is not necessarily a micro-statement. This conclusion can be illustrated via the example of the bracket  \(\{(0,+),(1,x),(2,y)\}\) whose notation has two symbols as parameters but is not a micro-statement. The second restriction is more important, which is that a micro-statement must have the capacity to be evaluated into a Boolean value, that is, \(\text{true}\) or \(\text{false}\). What is notable, the \textbf{ evaluation} process is not declared inside the representation system, whose definition comes below. All micro-statement brackets forms the \textbf{ Micro-Statement }sub-category of \(\text{Bra}(\mathcal{C})\) and is annotated as \(\text{Mic}(\mathcal{C})\).
	\end{definition}

@@

		\begin{equation}
			\begin{gathered}
				\mathit{e}\mathit{v}\mathit{a}\ell :\text{Ob}(\text{Mic}(\mathcal{C}))\to \mathcal{B}\\
				\mathit{m}\overset{\mathit{e}\mathit{v}\mathit{a}\ell }{\mapsto }\mathit{e}\mathit{v}\mathit{a}\ell (\mathit{m})
			\end{gathered}
		\end{equation}

		The Boolean value \(\mathit{e}\mathit{v}\mathit{a}\ell (\mathit{m})\in \{0,1\}\) is called the \textbf{ evaluation result} of micro-statement. If for bracket \(\mathit{m}\) exists a morphism to \(\mathcal{B}\) that satisfies the definition of evaluation, then we say that \(\mathit{m}\) is \textbf{ evaluatable}. That is, if it satisfies the first restriction of being a micro-statement as well, it is a micro-statement.
	\end{definition}

@@

	\section{The Standardized Principles for Derivation of Statements}

@@

	The discussion below calls the \(\text{Mic}(\mathcal{C})\) category the \textbf{ micro-statement pool}, or \textbf{ pool} for short. The morphisms inside the micro-statements pool are declared for representation of implication relationships. It is obvious and elementary that,

	\begin{equation}
		\forall \alpha ,\beta \in \text{Ob}(\text{Mic}(\mathcal{C})), \forall \left|\text{Hom}_{\text{Mic}(\mathcal{C})}(\alpha ,\beta )\right|=1
	\end{equation}

@@

	%% \pmb{ Definition.}
	\begin{definition}
		A \textbf{ derivation} is a set of ordered pairs of ordinals and categories in the form below.

@@

	%% \pmb{ Definition.}
	\begin{definition}
		A \textbf{ step of derivation} is a map existed on the derivation set \(\mathcal{D}\), mapping from a pair to another, whose ordinal increases by \(1\). This map is annotated using script word \(\mathit{s}\mathit{t}\mathit{e}\mathit{p}\). The form is shown below:

>>>>

\documentclass{aims}
\usepackage{txfonts, verbatim}
\usepackage{amsmath}	
\usepackage{flexisym, breqn}	
\usepackage{amssymb, graphics, setspace}	
\usepackage{tikz, tikz-cd}	
\usepackage{flowchart}	
\usepackage{float, booktabs}	
\usepackage{algorithmicx, algorithm,algpseudocode}	
\usepackage{blindtext}	
\usepackage{url}	
\usepackage[pagewise]{lineno}
\usepackage[comma, square, sort, numbers]{natbib}

@@

\renewcommand{\bibnumfmt}[1]{#1.}

\def\typeofarticle{Research article}
\def\currentvolume{8}
\def\currentissue{8}
\def\currentyear{2023}
\def\currentmonth{}
\def\ppages{xxxx--xxxx.}
\def\DOI{ 10.3934/math.2023xxx}
\def\Received{08 January 2023}
\def\Revised{29 April 2023}
\def\Accepted{19 May 2023}
\def\Published{x May 2023}
\setcounter{page}{1}
\hyphenpenalty=10000
%\usepackage{cite}
\captionsetup[figure]{font=normalsize,labelfont=bf,singlelinecheck=true}
\captionsetup[table]{font=normalsize,labelfont=bf,singlelinecheck=true}

@@

\begin{document}
	\title{A new type of generic, self-evolving and efficient automated deduction algorithm based on category theory}
	\author{%
		Zijian Wang\affil{1}
		and Xinhui Shao\affil{2,*}
	}
	\shortauthors{the Authors}
	\address{%
		\addr{\affilnum{1}}{Northeast Yucai School, Zhenxing St. 9-5, Heping District, Shenyang, Liaoning, China.}
		\addr{\affilnum{2}}{Department of Mathematics, College of Sciences, Northerneastern University, Shenyang, Liaoning, China. }
		\corraddr{Email: shaoxinhui@mail.neu.edu.cn.}
	}

	\begin{abstract}
	In this article a new type of generalized, self-evolving and efficient automated statement proof algorithm based on new data structures, i.e., brackets and map graphs
	and new algorithms is presented. The brackets structure provides an elegant low-knowledge representation of mathematical concepts. The map graphs offer an efficient machine-learning method which let the computer learn knowledge while proving. Additionally, the new finding is totally built on the category theory. Furthermore, a prototype of the program is given and examined for performance.
	\end{abstract}

	\keywords{
		{automatic prover; theorem prover; algorithm; category theory; automatic deduction; automatic reasoning}
		\newline
		\textbf{Mathematics Subject Classification:} 03B35, 68V15, 18-00, 18-04, 68W99
	}

@@

	\section{Introduction}
	During the long period of development of the research on automated theorem provers, there have already existed a great number of research and implementation on proofs focusing on a specific mathematical subject, such as algebra equations (for example, Wolfram Mathematica{'}s Find Equation Proof function \cite{Wolfram2019}) or geometrical theorems (for example, the Geometry Expert or GEX \cite{Gao1998} of Key Laboratory of Mathematics Mechanization, Chinese Academy of Sciences). Some relatively new works in this aspect includes Microsoft{'}s Lean prover \cite{Moura2021} and Z3 \cite{Moura2008} algorithm.

@@

	When we humans think of mathematical problems and perform proofs, we do not follow purely logical ways like complex stuff like Cooper{'}s algorithm. Instead, we just perform tries to seek breakthrough points using his knowledge in a diversified thought. Why cannot programs do things like that? Why can not they perform some sort of knowledge transferring? Carry this question and in experimental and curious attitude, we conducted the research on this topic and have found a utility to do the task: The category theory.

@@

\noindent	\textit{ Structure of the paper}

	The paper mainly consists of seven sections. The Introduction section demonstrates the background of the research and fundamental opinions around it. The Preliminaries section, made up of two subsections, claims to minimized pre-knowledge required to understand the paper and the symbols we select to use. The third section defines a set of mathematical structures that will be used by the algorithm. The forth section explains the detailed workflow procedures of the algorithm. The next section claims the conclusions of the research and the to-do improvements in the future. Then the algorithm is examined using several experiments and benchmarks to test the performance through the corresponding computer program in the thereupon. Finally the Acknowledgments section expresses my gratitude to the help and the References section claims the referential resources used while conducting the project.

@@

	\subsection{Notations and conventions}

@@

	To avoid misunderstandings, {the Zermelo-Fraenkel set theory} or ZFC as short is utilized to be the set system, with Grothendieck universe concepts added \cite{Li2019}.

@@

	\subsection{Pre-knowledge}

@@

	%%\pmb{ Axiom.} The Selection Axiom.
	\begin{axiom}
		The selection axiom.

@@

	%%\pmb{ Theorem. }
	\begin{theorem}
		The Zermelo{'}s Well-Ordering Theorem \cite{Li2019}.

@@

	\begin{equation*}
		X_{n+1}=(\left(a X_n+c\right) \bmod M).
	\end{equation*}

@@

	\begin{equation*}
		M=2^{32},a=1103515245, c=12345.
	\end{equation*}

@@

	\section{The computerized representation of mathem-atical structures}

	Before more specific discussion, we select Grothendieck universe \(\mathcal{U}\) \cite{Li2019} to avoid set theory paradoxes. Besides, we define meta category \(\mathcal{C}\) where all discussions take place. There are briefly three kind of objects in \(\mathcal{C}\): symbols, notations and brackets. All symbols in \(\mathcal{C}\) forms sub-category \(\text{Sym}(\mathcal{C})\) called the{ Symbol Subcategory}. All notations in \(\mathcal{C}\) forms \(\text{Not}(\mathcal{C})\) and all brackets forms \(\text{Bra}(\mathcal{C})\), called the{ Notation Subcategory} and the{ Bracket Subcategory}. That is,

	\begin{equation}
		\mathcal{C}=\text{Sym}(\mathcal{C})\cup \text{Not}(\mathcal{C})\cup \text{Bra}(\mathcal{C}).
	\end{equation}

@@

	%% \pmb{ Definition.} 
	\begin{definition}
		A{ bracket} \(\beta\) is defined as a set of ordered pairs in the form of below:
				\begin{equation}
			\beta \text{:=}\left\{(i,x)\left|i\in \text{On}_{\geq 1}\right.,x\in \text{Sym}(\mathcal{C})\cup \text{Not}(\mathcal{C})\cup \text{Bra}(\mathcal{C})\right\}
		\end{equation}
\(\beta\) is valid if and only if every element of \(\beta\), its left element is unique. We define filtered subsets of \(\beta\). The {Symbol Subset} of \(\beta _{\mathcal{S}}\text{:=}\left\{t\in \beta \left|t_{\mathit{r}}\in \text{Sym}(\mathcal{C})\right.\right\}\). Following this way, the {Notation Subset} \(\beta _{\mathcal{N}}\) and the {Bracket Subset} \(\beta _{\mathcal{B}}\) are defined as well. There are two types of brackets: The first type is called a {Symbol Holder} where \(\beta =\{(i,A)\},i\in \mathbb{Z}_{\geq 1},A\in \text{Sym}(\mathcal{C})\). The second type is called a {Compositor} where

		\begin{equation}
			\begin{split}
				\beta =\{(j,\mathcal{N})\}\cup \{(i,x)|i\in \text{On}_{\geq 1},\\ x\in \text{Sym}(\mathcal{C})\cup \text{Bra}(\mathcal{C})\},\forall
				t\in \beta ,j\in \text{On}_{[1,t_{\ell }]}\}.
			\end{split}
		\end{equation}
	\end{definition}

@@

	%% \pmb{ Definition.} 
	\begin{definition}
		Two bracket \(\alpha\) and \(\beta\), are thought to be {isomorphic} (noted as \(\alpha \simeq \beta\)) if they satisfy the following restrictions:

		First, \(|\alpha |=|\beta |\) indicating the two brackets have same cardinal numbers. Second, all right elements sorted in the order defined by the sort of the left pair elements, correspondingly, are either same or symbols with the same type. Otherwise, the two brackets are not isomorphic, noted as \(\alpha \not{\simeq}\beta\).
	\end{definition}

@@

	%% \pmb{ Definition.} 
	\begin{definition}
		A {notation} \(\mathcal{N}\) is defined as an object in \(\text{Not}(\mathcal{C})\) which is a sub-category of \(\mathcal{C}\). The \(\text{Ob}(\text{Not}(\mathcal{C}))\) set can be mapped to \(\text{On}_{\geq 0}\) class, indicating the number of parameters that a notation take. In which,

		\begin{equation}
			\begin{gathered}
				\mathit{p}:\text{Ob}(\text{Not}(\mathcal{C}))\to \text{On}_{\geq 0}\\
				\mathcal{N}\overset{\mathit{p}}{\mapsto}n.
			\end{gathered}
		\end{equation}

		In that case if \(n=0\) then we say \(\mathcal{N}\) is a{ type} and if \(n>0\) then \(\mathcal{N}\) is an{ operator}. For instance, obviously, \(\mathit{p}(+)=2\) and \(\mathit{p}(\neg )=1\). A notation\(\mathcal{N}\) is called{ finite} if \(\mathit{p}(\mathcal{N})<\omega\), and otherwise \(\mathcal{N}\) can have infinite number of symbols as parameters, when the notation is called to be{ infinite}.
	\end{definition}

@@

	%% \pmb{ Definition.}
	\begin{definition}
		A{ symbol} \(\mathcal{S}\) is defined as an object in \(\text{Sym}(\mathcal{C})\) which is a sub-category of \(\mathcal{C}\). There exists a functor from \(\text{Sym}(\mathcal{C})\) to \(\text{Not}(\mathcal{C})\):

@@

		\noindent where \(\nu (\mathcal{S})\) is the{ corresponding notation} of \(\mathcal{S}\) and must satisfy \(\forall \mathcal{S}\in \text{Sym}(\mathcal{C}),\mathit{p}(\nu (\mathcal{S}))\) \(= 0\), indicating all corresponding notations are types instead of operators. For convenience and precision, the text that meaning creating a symbol \(\mathcal{S}\) whose corresponding notation is \(\mathcal{N}\)can and should be written in the form below.

		\begin{equation}
			\mathcal{S}\in \text{Ob}(\text{Sym}(\mathcal{C}))\land \mathit{v}(\mathcal{S})==\mathcal{N}.
		\end{equation}

@@

		Two brackets are thought to be{ equal} when the sequences of \(t_{\mathit{r}}\), sorted via the ordering of \(t_{\ell }\) are the same and this relationship constructs a equivalence morphism between the two in the \(\text{Bra}(\mathcal{C})\) category, noted as below:

		\begin{equation}
			\epsilon :\alpha \equiv \beta.
		\end{equation}
	\end{definition}

@@

	%% \pmb{ Definition.}
	\begin{definition}
		A notation \(\mathcal{N}\) is called being{ inherited} from notation \(\mathcal{M}\) (or we say \(\mathcal{N}\) is{ a kind of} \(\mathcal{M}\)) when there exists such morphism between the two in \(\text{Not}(\mathcal{C})\):

		\begin{equation}
			h\in \text{Mor}(\text{Not}(\mathcal{C})): \mathcal{M}\to \mathcal{N}.
		\end{equation}

@@

	\begin{equation*}
		\sum _{n=0}^{\infty } x^n=\frac{1}{1-x}, \text{for} |x|<1.
	\end{equation*}

	First, we need to observe what notation is needed by the construction. Apparently, we need to at least define these notations: \(\text{inf}\), \(\text{int}\), \(\text{num}\),\textit{  }\textit{ \(\sum\)}, \(=\), \({}^{\wedge}\), \(/\), \(-\), \(\text{abs}\), \(<\) and \(\text{for}\), where \(\text{abs}\) stands for the absolute value function. However, in this neat example, the concept of function is not needed to be defined. Additionally, as the constructed stuff only needs to demonstrate the equation itself instead of the principles behind the equality, there is no necessity for the definition of notation \(+\). Note that manifestly \(\text{int} \triangleleft | \text{num}\). Table  \ref{table-1} demonstrates the number of parameters taken by the notations.

	\begin{table}[h]
		\centering
		\caption{The table for $\mathit{p}(\mathcal{N})$.}
		\begin{tabular}{ccccccccccc}
			\toprule
			$\mathcal{N}$ & int & num & inf & $\sum$ & $=$ & $/$ & - & abs & $<$ & for \\
			\midrule
			$\mathit{p}$ & $0$ & $0$ & $0$ & $3$ & $2$ & $2$ & $2$ & $1$ & $2$ & $2$ \\
			\bottomrule
		\end{tabular}
		\label{table-1}
	\end{table}

@@

	\begin{equation*}
		\begin{aligned}
			\pmb{1} &\in& \text{Ob}(\text{Sym}(\mathcal{C}))\land \mathit{v}(\pmb{1})=\text{number}\\
			\pmb{\infty } &\in& \text{Ob}(\text{Sym}(\mathcal{C}))\land \mathit{v}(\pmb{\infty })=\text{infinity}\\
			\pmb{x} &\in& \text{Ob}(\text{Sym}(\mathcal{C}))\land \mathit{v}(\pmb{x})=\text{number}\\
			\pmb{n} &\in& \text{Ob}(\text{Sym}(\mathcal{C}))\land \mathit{v}(\pmb{n})=\text{integer}\triangleleft |\text{number}\\
		\end{aligned}
	\end{equation*}
	\begin{equation*}
		\begin{aligned}
			\alpha &=& \{(0,\text{for}),(1,\beta ),(2,\gamma )\}\\
			\beta &=& \{(0,=),(1,\delta ),(2,\epsilon )\}\\
			\gamma &=& \{(0,<),(1,\zeta ),(2,\pmb{1})\}\\
			\delta &=& \{(0,\sum ),(1,\eta ),(2,\pmb{\infty }), (3,\theta )\}\\
			\epsilon &=& \{(0,/),(1,\pmb{1}),(2,\iota )\}\\
			\zeta &=& \{(0,\text{abs}),(1,\pmb{x})\}\\
			\eta &=& \{(0,=),(1,\pmb{n}),(2,\pmb{1})\}\\
			\theta &=& \{(0,{}^{\wedge}),(1,\pmb{x}),(2,\pmb{n})\}\\
			\iota &=& \{(0,-),(1,\pmb{1}),(2,\pmb{x})\}.
		\end{aligned}
	\end{equation*}

@@

	\begin{equation}
		\begin{split}
			\alpha = \{(0,\text{for}),(1,\beta ),(2,\{(0,<),(1,\{(0,\text{abs}),\\(1,\pmb{x})\}),(2,\pmb{1})\})\}\hfill\\
			\beta = \{(0,=),(1,\delta ),(2,\{(0,/),(1,\pmb{1}),(2,\{(0,-),\\(1,\pmb{1}),(2,\pmb{x})\})\})\}\hfill\\
			\delta = \{(0,\sum ),(1,\{(0,=),(1,\pmb{n}),(2,\pmb{1})\}),(2,\pmb{\infty }), (3,\\\{(0,{}^{\wedge}),(1,\pmb{x}),(2,\pmb{n})\})\}.\hfill\\
		\end{split}
	\end{equation}

@@

	Another issue is about the recognition between majorly two types of brackets: The type of bracket that purely serves as a brick for constructing mathematical expressions and the type of bracket that forms the thing that former mathematics call them statements (for instance, \(\{(0,=),(1,x),(2,y)\}\) or the expression for the Pythagorean theorem). In this system for representation, the second sort of bracket is called{ micro-statements}, whose precise definition comes below.

@@

		It is essential to pay attention to that a bracket with 2-parameter notation is not necessarily a micro-statement. This conclusion can be illustrated via the example of the bracket  \(\{(0,+),(1,x),(2,y)\}\) whose notation has two symbols as parameters but is not a micro-statement. The second restriction is more important, which is that a micro-statement must have the capacity to be evaluated into a Boolean value, that is, \(\text{true}\) or \(\text{false}\). What is notable, the{ evaluation} process is not declared inside the representation system, whose definition comes below. All micro-statement brackets forms the{ Micro-Statement }sub-category of \(\text{Bra}(\mathcal{C})\) and is annotated as \(\text{Mic}(\mathcal{C})\).
	\end{definition}

@@

		\begin{equation}
			\begin{gathered}
				\mathit{e}\mathit{v}\mathit{a}\ell :\text{Ob}(\text{Mic}(\mathcal{C}))\to \mathcal{B}\\
				\mathit{m}\overset{\mathit{e}\mathit{v}\mathit{a}\ell }{\mapsto }\mathit{e}\mathit{v}\mathit{a}\ell (\mathit{m}).
			\end{gathered}
		\end{equation}

		The Boolean value \(\mathit{e}\mathit{v}\mathit{a}\ell (\mathit{m})\in \{0,1\}\) is called the{ evaluation result} of micro-statement. If for bracket \(\mathit{m}\) exists a morphism to \(\mathcal{B}\) that satisfies the definition of evaluation, then we say that \(\mathit{m}\) is{ evaluatable}. That is, if it satisfies the first restriction of being a micro-statement as well, it is a micro-statement.
	\end{definition}

@@

	\section{The standardized principles for derivation of statements}

@@

	The discussion below calls the \(\text{Mic}(\mathcal{C})\) category the{ micro-statement pool}, or{ pool} for short. The morphisms inside the micro-statements pool are declared for representation of implication relationships. It is obvious and elementary that,

	\begin{equation}
		\forall \alpha ,\beta \in \text{Ob}(\text{Mic}(\mathcal{C})), \forall \left|\text{Hom}_{\text{Mic}(\mathcal{C})}(\alpha ,\beta )\right|=1.
	\end{equation}

@@

	%% \pmb{ Definition.}
	\begin{definition}
		A{ derivation} is a set of ordered pairs of ordinals and categories in the form below.

@@

	%% \pmb{ Definition.}
	\begin{definition}
		A{ step of derivation} is a map existed on the derivation set \(\mathcal{D}\), mapping from a pair to another, whose ordinal increases by \(1\). This map is annotated using script word \(\mathit{s}\mathit{t}\mathit{e}\mathit{p}\). The form is shown below:
